Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-11 ms.tex
Update Section 4
From 03449a2:
============

In ms.tex,

(*) Update Section 4

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling (bottom) with no thermal noise fluctuations (Paper~I) shown for reference. In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent. The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the power pattern pointed at the zenith.

@@

The key defining feature of the {\it pitchfork} signature is an enhancement in foreground power near the horizon limits. In the individual snapshot, similar to the one used in our original study, faint features are visible near the horizon limits. But the high level of thermal fluctuations makes their significance marginal. In contrast, the dynamic range (in power spectrum units) in the averaged data (middle) is a factor $\gtrsim 10$ higher relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent. We now note that faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.

>>>>

Figure~\ref{fig:delay-spectra} shows the delay spectra obtained from a single snapshot of MWA data (top), averaging LST aligned delay spectra from 12 individual snapshots from MWA observations on different nights (middle), and from modeling with no thermal noise fluctuations shown for reference (bottom). In all panels, the {\it foreground wedge} bounded by horizon limits (white dotted lines) is prominent. The bright branch of power at $\tau=0$ corresponds to foreground emission from the main lobe of the antenna power pattern pointed at the zenith.

@@

The key defining feature of the {\it pitchfork} signature is an enhancement in foreground power near the horizon limits. In the individual snapshot, similar to the one used in our original study, faint features are visible near the horizon limits. But the high level of thermal fluctuations makes their significance marginal. In contrast, the dynamic range in the averaged data (middle) is a factor $\gtrsim 10$ higher (in delay power spectrum) relative to that in a single snapshot (top), and is consistent with the improvement expected from averaging 12 independent snapshots. With this improvement in sensitivity, the foreground power near the horizon limits (white dotted lines) appears $\gtrsim 10$ times more prominent. Faint horizontal features appear at $\tau = \pm 0.78\,\mu$s also as a result of lowering thermal fluctuations which is not seen in the single snapshot, thus confirming effective lowering of thermal fluctuations. We identify these faint features as the response in delay space of the MWA coarse band edges flagged periodically every 1.28~MHz.
